### 2013-02-13 draft.tex
save

\begin{tabular}{lr}
Student: & Kostenko Dmitry \\
Group: & 472SE \\
Argument Consultant: & Prof. Ivan. M. Gostev, PhD \\
Style and Language Consultant: & Tatiana A. Stepantsova
\end{tabular}

@@

Examples of such an approach: ****\

Our work uses a different approach. We suggest an alternative method for counting vehicles without the pre-modelled background.
It is based on the differences sum  of the neighbouring frames of a video sequence and highlighting the connected areas.

\newpage
\section{Problem statement}
%Резальтатом данной главы будет являтся список требований к алгоритму.
%Для формальности приведем некоторые определения.
%Т.к. видео - это последовательность кадров, то в каждый момент времени мы имеем один кадр, называемый текущим.
%Если кадр i - текущий кадр, то кадр (i-1) - предыдущий.
%Объектами переденго плана будем считать любые движущиеся объекты (транспортные средства, деревья, люди).
%Определение объекта, как движущегося, зависит от характеристик камеры и окружающей обстановки.
%Поэтому движущимися объектами назовем те объекты, которые меняют свое положение на текущем кадре, относительно предыдущего кадра.
%Движущийся объект перед камерой или движущиеся камера в неподвижной обстановке ведет к изменения изображения.
%Изображение видимого движения объекта называется оптическим потоком.
%Существует несколько методов вычисления оптического потока.
%Лукас и Канаде предложили дифференциальный подход.
%О нем будет рассказано позже.
%Теперь перейдем к постановке задачи.
%Одна из наиболее важных задач в видео наблюдении состоит из идентификации объекта интереса и отслеживание его траектории в последующих кадрах.
%Эта задача может быть разбита на подзадачи.
%Первое, необходимо обнаружить объекты интереса или объекты переднего плана.
%Обнаружение объектов интереса подразумевает под собой отделение переднего плана от фона на изображении.
%После того, как мы это сделали мы получим бинарную карту движущихся объектов на изображении.
%Далее необходимо понять, какие из движущихся объектов являются автотранспортными средствами, а какие не являются таковыми. 
%Так как на изображении могут двигаться не только объекты переднего плана, но и объекты заднего плана (например ветви деревьев), то появляется необходимость борьбы с данным явлением.
%Для этого ограничим на изображении область, в которой мы и будем вести видеонаблюдение. %рисунок
%Такой областью лучше всего выделить хорошо просматриваемый промежуток автодороги.
%Затем следить за изменениями координат обектов интереса в последующих кадрах.
%Для вычисления оптического потока необходимо сделать несколько предположений.
%1) изображение - это непрерывная функция от двух переменных;
%2) яркость объекта остается неизменной в небольшой промежуток времени;
%3) отслеживаеммый объект на новом кадре будет расположен на небольшом расстоянии относительно предыдущего кадра.
%Первое предположение дает нам возможность использовать методы математического анализа и позволяет производить матемстические операции над изображением.
%Второе предположение существует потому, что мы живем в реальном мире, в котором  обхекты не могут мгновенно перемещаться на большие расстояния.
%Третье предположение необходимо потому что мы не сможем без него отслеживать объект.

In this chapter we will state the set of requirements for the algorithm.
As a formality we will state several definitions first.
As any video is a sequence of frames, every moment in time we have one frame called the current frame.
If the current frame is defined as i, the previous frame will be defined as (i-1).
We will consider all the moving objects such as vehicles, trees, humans as the foreground.
Whether the object is considered as a moving one depends on the camera properties and the environment.
So we define moving objects as the ones that shift their position in the current frame, relatively to previous frame.
When the camera moves, or the object in its focus, it leads to the image changes.
The description of the movements which can be seen is called the optical flow.
There are several methods for calculating this flow.
Lucas and Kanade developed one of them, using differential approach \cite{lucaskanade}.
It will be described later in this paper.
Now let us move to the problem statement.
One of the most important problems of video surveillance is identifying the object of interest and following its trajectory through the sequence of the following frames.
This problem can be partitioned into several sub-problems.
In the beginning it is necessary to find the objects of interest, which can also be called the foreground objects.
Finding these objects involves separation of the foreground from the background of the image.
As a result we get a binary map of the moving objects.
After that we need to separate vehicles from other moving objects such as trees or humans. 
For doing so we limit the area in which we will track movement.
%и назовем ее областью интереса
A good choice will be a well-observed part of a highway. 
Then we need to track the changes in objects of interest coordinates in the following frames.

@@

Now let us move to the descripton of the algorithm.

@@

It is necessary to consider that the method of subtracting the previous frame from the current frame gives good response near the moving object border. 
However, inside the objects borders the response is NOT SO GOOD.
If the vehicle is relatively large, the probability of its recognition as an object of the foreground is low.

@@

\newpage
\section{Bibliography}
\begin{thebibliography}{99}
\bibitem{lucaskanade} An Iterative Image Registration Technique with an Application to Stereo Vision, Bruce D. Lucas Takeo Kanade, Computer Science Department Carnegie-Mellon University Pittsburgh, Pennsylvania 15213

\bibitem{realtime_vehicle_detection} Real Time Vehicle Detection and Counting Method for Unsupervised Traffic Video on Highways, Mrs. P.M.Daigavane † and Dr. P.R.Bajaj ††, S. D. College of Engineering, M.S., INDIA
\end{thebibliography}

\newpage
\section{Appendix}

\begin{figure}[ht]
\centering
\tikzstyle{line} = [draw, -stealth, thick]
\tikzstyle{block} = [draw, rectangle, fill=white!50, text width=8em, text centered, minimum height=13mm, node distance=8em]
\begin{tikzpicture}

\node [block] (video_clip) {input video clip};

\node [block, below of=video_clip, yshift=2em] (to_gray) {transform frames to grayscale};

\node [block, below of=to_gray, yshift=2em, xshift=-3em] (frame_i) {frame i};
\node [block, left of=frame_i, xshift=-1em] (frame_i_plus_one) {frame i+1};
\node [block, right of=frame_i, xshift=0em] (frame_i_plus_two) {frame i+2};
\node [block, right of=frame_i_plus_two, xshift=1em] (frame_i_plus_three) {frame i+3};

\node [block, below of=to_gray, yshift=-5em] (sum_of_diff) {the sum of frame substractions};

\node [block, below of=sum_of_diff, yshift=2em] (binarization) {binarization};

\node [block, below of=binarization, yshift=2em] (segmentation) {image segmentation};

\node [block, below of=segmentation, yshift=2em, xshift=-6em] (detection) {vehicle detection};
\node [block, below of=segmentation, yshift=2em, xshift=6em] (tuning) {vehicle tuning};

\node [block, below of=segmentation, yshift=-4em] (counting) {vehicle counting};
%arrows
\path [line] (video_clip) -- (to_gray);
\path [line] (to_gray) -- (frame_i);
\path [line] (to_gray) -- (frame_i_plus_one);
\path [line] (to_gray) -- (frame_i_plus_two);
\path [line] (to_gray) -- (frame_i_plus_three);

\path [line] (frame_i) -- (sum_of_diff);
\path [line] (frame_i_plus_one) -- (sum_of_diff);
\path [line] (frame_i_plus_two) -- (sum_of_diff);
\path [line] (frame_i_plus_three) -- (sum_of_diff);

\path [line] (sum_of_diff) -- (binarization);

\path [line] (binarization) -- (segmentation);

\path [line] (segmentation) -- (detection);
\path [line] (segmentation) -- (tuning);

\path [line] (detection) -- (counting);
\path [line] (tuning) -- (counting);
\end{tikzpicture}
\end{figure}

>>>>

\hfill Word count: 2843

\begin{tabular}{lr}
Student: & Kostenko Dmitry \\
Group: & 472SE \\
Argument Consultant: & Prof. Ivan. M. Gostev, D.Sc. \\
Style and Language Consultant: & Tatiana A. Stepantsova
\end{tabular}

@@

Examples of such an approach are presented by Mrs. P.M.Daigavane and Dr. P.R.Bajaj \cite{realtime_vehicle_detection} and Dule Shu \cite{vehicle_tracking}.
Our work uses a different approach. We suggest an alternative method for counting vehicles without the pre-modelled background.
It is based on the differences sum  of the neighbouring frames of a video sequence and highlighting the connected areas.

\newpage
\section{Problem statement}
%Резальтатом данной главы будет являтся список требований к алгоритму.
%Для формальности приведем некоторые определения.
%Т.к. видео - это последовательность кадров, то в каждый момент времени мы имеем один кадр, называемый текущим.
%Если кадр i - текущий кадр, то кадр (i-1) - предыдущий.
%Объектами переденго плана будем считать любые движущиеся объекты (транспортные средства, деревья, люди).
%Определение объекта, как движущегося, зависит от характеристик камеры и окружающей обстановки.
%Поэтому движущимися объектами назовем те объекты, которые меняют свое положение на текущем кадре, относительно предыдущего кадра.
%Движущийся объект перед камерой или движущиеся камера в неподвижной обстановке ведет к изменения изображения.
%Изображение видимого движения объекта называется оптическим потоком.
%Существует несколько методов вычисления оптического потока.
%Лукас и Канаде предложили дифференциальный подход.
%О нем будет рассказано позже.
%Теперь перейдем к постановке задачи.
%Одна из наиболее важных задач в видео наблюдении состоит из идентификации объекта интереса и отслеживание его траектории в последующих кадрах.
%Эта задача может быть разбита на подзадачи.
%Первое, необходимо обнаружить объекты интереса или объекты переднего плана.
%Обнаружение объектов интереса подразумевает под собой отделение переднего плана от фона на изображении.
%После того, как мы это сделали мы получим бинарную карту движущихся объектов на изображении.
%Далее необходимо понять, какие из движущихся объектов являются автотранспортными средствами, а какие не являются таковыми. 
%Так как на изображении могут двигаться не только объекты переднего плана, но и объекты заднего плана (например ветви деревьев), то появляется необходимость борьбы с данным явлением.
%и назовем ее областью интереса
%Для этого ограничим на изображении область, в которой мы и будем вести видеонаблюдение. %рисунок
%Такой областью лучше всего выделить хорошо просматриваемый промежуток автодороги.
%Затем следить за изменениями координат обектов интереса в последующих кадрах.
%Для вычисления оптического потока необходимо сделать несколько предположений.
%1) изображение - это непрерывная функция от двух переменных;
%2) яркость объекта остается неизменной в небольшой промежуток времени;
%3) отслеживаеммый объект на новом кадре будет расположен на небольшом расстоянии относительно предыдущего кадра.
%Первое предположение дает нам возможность использовать методы математического анализа и позволяет производить матемстические операции над изображением.
%Второе предположение существует потому, что мы живем в реальном мире, в котором  обхекты не могут мгновенно перемещаться на большие расстояния.
%Третье предположение необходимо потому что мы не сможем без него отслеживать объект.

In this chapter we will state the set of requirements for the algorithm.
As a formality we will state several definitions first.
As any video is a sequence of frames, every moment in time we have one frame called the current frame.
If the current frame is defined as i, the previous frame will be defined as (i-1).
We will consider all the moving objects such as vehicles, trees, humans as the foreground.
Whether the object is considered as a moving one depends on the camera properties and the environment.
So we define moving objects as the ones that shift their position in the current frame, relatively to previous frame.
When the camera moves, or the object in its focus, it leads to the image changes.
The description of the movements which can be seen is called the optical flow.
There are several methods for calculating this flow.
Lucas and Kanade developed one of them, using differential approach \cite{lucaskanade}.
It will be described later in this paper.
Now let us move to the problem statement.
One of the most important problems of video surveillance is identifying the object of interest and following its trajectory through the sequence of the following frames.
This problem can be partitioned into several sub-problems.
In the beginning it is necessary to find the objects of interest, which can also be called the foreground objects.
Finding these objects involves separation of the foreground from the background of the image.
As a result we get a binary map of the moving objects.
After that we need to separate vehicles from other moving objects such as trees or humans. 
For doing so we limit the area in which we will track movement.
A good choice will be a well-observed part of a highway. 
Then we need to track the changes in objects of interest coordinates in the following frames.

@@

Now let us move to the description of the algorithm.

@@

It is necessary to consider that the method of subtracting the previous frame from the current frame gives good response near the moving object border. 
However, inside the objects borders the response is bad.
If the vehicle is relatively large, the probability of its recognition as an object of the foreground is low.

@@

\renewcommand{\refname}{}
\newpage
\section{References}
\begin{thebibliography}{99}
\vspace*{-1cm}

\bibitem{realtime_vehicle_detection}
Mrs. P.M.Daigavane and Dr. P.R.Bajaj. 
(2010). 
Real Time Vehicle Detection and Counting Method for Unsupervised Traffic Video on Highways.
\textit{IJCSNS International Journal of Computer Science and Network Security, VOL.10 No.8}.
pp. 80-82.

\bibitem{vehicle_tracking}
Dule Shu.
Vision based Vehicle Tracking using a high angle camera.
\textit{Raúl Ignacio Ramos García}

\bibitem{lucaskanade} 
Bruce D. Lucas, Takeo Kanade. 
(1981). 
An Iterative Image Registration Technique with an Application to Stereo Vision. 
\textit{Proceedings of Imaging Understanding Workshop}. 
pp. 121-130.

\end{thebibliography}
